---
output: github_document
---

#  Supplementary material for "3D point cloud semantic segmentation through functional data analysis"

Supplementary codes and data used in the paper "*3D point cloud semantic segmentation through functional data analysis*".


Please cite this paper as:

```
@article{oviedo2023PointCloud,
  title={3D point cloud semantic segmentation through
functional data analysis},
  author={Oviedo de-la Fuente, Manuel, Cabo, Carlos, Roca-Pardiñas, Javier, Loudermilk, Lousie and Ordóñez Celestino},Accepted in JABES
  year={2023}
}
```

# Installation  
In order to use paper implementation and run all files (numerical and real example), the following prerequisites are needed:


## 1. `fda.usc` package
<!--To install `fda.usc.devel` package (devel version of `fda.usc`) from Github with (2023/03/29):

```{r , eval = FALSE}
#install.packages("remotes")
remotes::install_github("moviedo5/FDA_3D_Point_Cloud/fda.usc.devel")
# install.packages("devtools")
# require(devtools)
# devtools::install_github("moviedo5/FDA_3D_Point_Cloud/pkg/fda.usc.devel")
```
-->

Our proposed method is  available in the `fda.usc` package (devel version) through the functions `classif.gsam.vs()` and `classif.ML.vs()`.


## 2. `PointNet` model 

PointNet was improved using a hierarchically approach called PointNet++ [9].

Referencia a github

Qi R, Yi l, Su H, Guibas LJ (2017) "PointNet++: Deep hierarchical
feature learning on point sets in a metric space", Proc. Adv. Neural Inf.
Process. Syst. 30 (NIPS), pp. 5105-5114


##  3. `DGCNN` model

DGCNN is a deep learning (DL) model for point cloud classification and semantic segmentation

Referencia a github

Wang Y, Yongbin S, Ziwei L, Sarma S Bronstein M, Solomo J (2018)
Dynamic Graph CNN for Learning on Point Clouds. ACM Transactions
on Graphics 38 2018 doi = 10.1145/3326362

<!--# Simulation (Numerical Studies)

+ `./inst/script/Simulation.R`: Code for main simulation.
  
```{r , eval =T,message=F,warning=F}
library(fda.usc.devel)
# source("./R/Simulation.R")
```
-->

# Real Data Application: 3D cloud point

Our case study example is 3D cloud point.


```{r , eval=T,message=F,warning=F}
library(fda.usc.devel)
load(file="./data/ldf.train.RData")
class(ldf.train)
n <- nrow(ldf.train$df)
# Response
table(ldf.train$df$class)
labels <- c("trunk","grass","branch+leaf","bush")
#levEn <- levels(ldf.train$df$class)
# predictor variables (multivariate)
predictors <- names(ldf.train$df[-c(1,2,3,5,6,831)])
# linear correlation between predictors
# dfcor <- cor(ldf.train$df[,c(predictors)])
```

Locations
```{r ,eval=T,message=F,warning=F,echo=T}
tab <- table(ldf.train$df$parcela)
iparcela <- c(0,2,6)
sum(tab[-iparcela]) # 100k,250k,500k
prop.table(tab)
ii <-1:400000
plot(ldf.train$df[ii,1:2],col=ldf.train$df$parcela[ii]+1,asp=T)
ii <- ldf.train$df$parcela %in% c(0,2,6) 
points(ldf.train$df[ii,1:2],col=1)
```

Functional mean curves for `Planarity` and `Sphericity` features (colored by class label).

```{r ,eval=T, message=F,warning=F, echo=F}
col1<- rgb(139/255,60/255,94/255,1)
col2<- rgb(193/255,129/255,0/255,1)
col3<- rgb(61/255,122/255,1/255,1)
col4<- rgb(50/255,133/255,182/255,1)
colores <- c(col1,col2,col3,col4)

lev <- levels(ldf.train$df$class)
####################################
# More pots
# Means by class and features
# f6 lineality
# f11 verticality
feature <- "Planarity"
#par(mfrow=c(2,3))
# dev.new()
par(mfrow=c(1,2))
nam <- names(ldf.train)[c(13,12,11,8,7,6)]
nam <- names(ldf.train)[c(7,12)]
ldf.train[[12]]$data <- ldf.train[[12]]$data - 1
var2<- c("Planarity","Sphericity")
variable <- levels(ldf.train$df$class)
for (j in 1:length(nam)){
  ####jpeg(paste0("Functional mean-",variable,".jpeg"))
  feature <- nam[j]
  for (indc in 1:4){
    #  indc <- 1
    ic <- ldf.train$df$class==lev[indc]
    aux <- subset(ldf.train,ic)
    
    if (indc==1) curvas <- func.mean(aux[[feature]])    else    
      curvas<- c(curvas,func.mean(aux[[feature]]))
  }
  for (indc in 1:4){  
    #mn <- paste0(variable,"-",levEn[indc])
    mn <- paste0(var2[j])
 
    if (indc==1) plot(curvas[1],main=mn,ylim=range(curvas$data),lwd=2,
                      ylab="",col=colores[1]) else 
        lines(curvas[indc],col=colores[indc],lwd=2)
  }
  #legend("topright",legend=c(lev),col=1:4,lwd=1,lty=1)
 ##### dev.off()
}
```


*This repository is under development, codes with examples will be included soon*
<!--## References-->

